---
title: "foofactors"
author: "Gokul Raj Suresh Kumar"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

A package to deal with the weird parts of factors. The implementation and documentation of `fbind()` and `freq_out` are purely based on Jennifer Bryan's `foofactors` package.

Loading the package and providing a preview of the data used:

```{r}
library(foofactors)
str(iris)
str(PlantGrowth)
```



Binding two factors via `fbind()`:

```{r}
fbind(iris$Species[c(1, 51, 101)], PlantGrowth$group[c(1, 11, 21)])
```

Obtaining a table of frequencies for the levels of a factor via `freq_out`:

```{r}
freq_out(iris$Species)
```

Detecting factors that should be characters via `is_char_factor`:

```{r}
is_char_factor(iris$Species)
```

Reordering levels of factor in descending order via `desc_reord`:

```{r}
levels(iris$Species)
levels(desc_reord(iris$Species))
```


